Pillar A1

### 2019-02-15 Baby Recommender.Rmd
inspect missing studentes

missing_students <- full_join(s.1,s.2, by = "Student.ID") %>% 
  filter(is.na(first.x)) %>%
  select(Student.ID)
```

>>>>

missing_students <- full_join(s.1,s.2, by = "Student.ID") %>% 
  filter(is.na(first.x)) %>%
  pull(Student.ID)

View(d_transcript%>%
  filter(`Student ID` %in% missing_students)) #students lost mostly only have external and core courses, there are a few internal courses missing: e.g. SSC1001
